---
pagetitle: "Home"
output: html_document
---

<style>
.fold-btn { float: left; }
</style>

<script type="text/javascript">
$(document).ready(function() {
  $(".fold").prepend("<button class=\"fold-btn\">read more</button>");
  $(".fold").children("code").toggle();
  $(".fold-btn").on("click", function() {
    if($(this).text() === "hide") {
      $(this).text("read more");
    } else {
      $(this).text("hide");
    }
    $(this).next("code").toggle("linear");
  })
});
</script>


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      tidy.opts=list(width.cutoff=80), 
                      tidy=TRUE,
                      comment=NA)
library(tidyverse)
library(plotly)
library(cowplot)
library(data.table)
library(DT)
library(visNetwork)
library(viridis)
library(DT)
theme_set(theme_cowplot(12))

org_colors <-
  c("Boston University" = "#CC0000",
    "Siemens Diagnostics" = "#009999",
    "Boston Children's Hospital" = "#003087",
    "University of Texas" = "#BF5700",
    "Genentech" = "#005596",
    "Leidos" = "#850F88")

elegen_color <- "#02c796"
```

## Howdy! 
This is the personal website for Cory DuPai. If you've found yourself here, I assume you're interested in learning more about me. Feel free to poke around and if you have any further questions, drop me a line at corydupai@gmail.com

<details>
<Summary> <b>-- Click text like this for more info --</b> </Summary>

Here is a quick rundown of my educational and employment background, feel free to poke around the CV tab for more detail.
</details>

```{r, out.width = "100%"}
shorten <- function(subz, xp_dt){
  xp_dt[, YS := `Year Start` + subz
      ][, YE := `Year End` - subz
      ][ YE > YS
      ][Organization %in% c(
        "Leidos",
        "University of Texas"), 
        `Year End` := `Year End` - 1
      ][Organization == "Leidos",
        `Year End` := NA_real_]
}

sub_range <- seq(0, 4, 0.1)

XP <- fread("Experience.csv")

XP <- lapply(sub_range, shorten, XP) %>% 
  rbindlist()

XP[, Organization := fct_inorder(Organization)]

XP_plot <- ggplot(XP) +
   geom_segment( aes(  
     group = Organization,
                      text = Event,
     Start = `Year Start`,
                       End = `Year End`,
                       x = YS, xend = YE, 
                      y = Y, yend = Y,
                      colour = Organization),
                 lineend = "round",
                 size = 5) +
  ylim(-1, -6.5) +
  scale_x_continuous(breaks = c(2009,2013,2014,2016,2019,2020,2021,2022),
                     labels = 
                       c(as.character(
                         c(2009,2013,2014,2016,2019,2020,2021)
                         ),
                         "Present")) +
  scale_colour_manual(values = org_colors) +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank())

p <- ggplotly(XP_plot,
              tooltip = c("text","group","Start","End"))  %>% 
  layout(legend = list(orientation = 'h',
                       xanchor = "left",
                       yanchor = "bottom"))


p %>% htmlwidgets::onRender("
function(el, x) {
// when hovering over an element, do something
el.on('plotly_hover', function(d) {
// extract tooltip text
let re1 = /.*Year Start: /;
let re2 = /<br.*/;
txt = d.points[0].data.text;
txt = txt.replace(re1,'');
txt = txt.replace(re2,'');
// image is stored locally
image_location = 'image/' + txt + '.jpg';
// define image to be shown
var img = {
// location of image
source: image_location,
// top-left corner
x: 0.3,
y: 0.75,
sizex: 0.2,
sizey: 0.2,
xref: 'paper',
yref: 'paper'
};
// show image and annotation
Plotly.relayout(el.id, {
images: [img]
});
})
}
")

```
